\input{preamble}

\begin{document}

\section*{CV - Eero Häihälä}
Printer friendly version

\cvheader{face-bw}{
    Insert a borderline narcissistic gloating blurb of text that has been ran
    through a thesaurus seven times to sound smart. Ideally it should assure
    the reader of my abilities in various circumstances with the slight caveat
    of proving nothing. 

    \vspace{10pt}

    I've gone to school for programming and professionally worked as a programmer.
    You can read more about that on
    \href{https://www.linkedin.com/in/eero-haihala/}{linkedin}. I'd like to
    work in games. See \href{https://haihala.github.io/portfolio}{my portfolio}
    for some highlights of what I've done so far.

    \vspace{10pt}

    You can reach me via email at
    \href{mailto:eero.haihala@gmail.com}{eero.haihala@gmail.com}
}

\section*{Skills}

\begin{skills}
    \skillitem{3}{Rust, TS/JS, Python, Bevy, Google cloud platform (ex-certified professional cloud architect), React, Web development, Docker, CI/CD, Shell scripts, Linux, Git}
    \skillitem{2}{Godot, Unity, Blender, C\#, Lua, Microsoft Azure, Terraform, Scrum, Agile, Teaching, Project management, B2B Customer communication, Java, SQL, Django, FastAPI, NodeJS, Svelte}
    \skillitem{1}{Unreal engine, C++, C, Android, AWS, Kotlin, Go, Zig, Haskell, PHP, MongoDB, \LaTeX, NextJS, Bun, Deno, Angular, HTMX}
\end{skills}

What I mean by each level:

\begin{etaremune}
    \item I'm as confident in these as I can be. Experience: 3-10 (average 5) years.
    \item What I think of as basic competence, but others keep telling me is a high bar. Experience: 1-8 (average 2) years.
    \item A week of (re-)learning away from level 2. Average experience: 3 months.
\end{etaremune}

There are a lot things I dabble in that didn't make the cut. I've hit the 50
skill limit on \href{https://www.linkedin.com/in/eero-haihala/}{linkedin} on
technical skills alone, and then had to cut some of them out to try to better
match the skill lists recruiters look for. This has the unfortunate side effect
of forgetting I know something if I don't actively use it.

\section*{Work experience}

\begin{Timeline}
	\timelineitem{Ongoing since 2021}{Lead software developer}{Vincit}
	\timelineitem{Three years (2022-2024)}{Head computer science teacher}{Päivölä School of Mathematics}
	\timelineitem{Five years (2018-2022)}{Occasional computer science lecturer}{Päivölä School of Mathematics}
	\timelineitem{Two years (2019-2020)}{Systems specialist}{Ambientia}
	% \timelineitem{Three months (2017)}{Software developer}{Intopalo, part of Insta group nowadays}
	\timelineitem{Two years (2014-2016)}{Trainee}{Nokia and Päivölä student innovation labs}
\end{Timeline}

\section*{Education}

\begin{Timeline}
	\timelineitem{Two years (2022-2024)}{Master of Science (Technology)}{Tampere University}
	\timelineitem{Five years (2016-2021)}{Bachelor of Science (Technology)}{Tampere University}
	\timelineitem{Two years (2014-2016)}{High school graduate}{Päivölä School of Mathematics}
\end{Timeline}

\end{document}

